Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-15 numerical-chemistry.tex
updating chemistry!

The primordial non-equilibrium chemistry routines used in \enzo\ were
first described by Abel et al. and Anninos et
al. \citep{abel97,anninos97}, but have been extended since then with
updated reaction rates and the inclusion of deuterium species.  These 
routines follow the non-equilibrium chemistry of a 
gas of primordial composition with 12 total species:  
$H$, $H^+$, $He$, $He^+$, $He^{++}$, $H^-$, $H_2^+$, $H_2$, $e^-$,
$D$, $D^+$, and $HD$.  (A separate, but related, module follows the
radiative heating and cooling of the gas from atomic and molecular line excitation,
recombination, collisional excitation, free-free transitions, Compton
scattering of the cosmic microwave background, as well as several
models for a metagalactic UV background that heat the gas via
photoionization and discussion -- see Section~\ref{sec.num.cooling}
for more details).  Depending on user parameters, one can follow
simply atomic species ($H$, $H^+$, $He$, $He^+$, $He^{++}$,  and
$e^-$), include those relevant for molecular hydrogen formation
($H_2$, $H_2^+$, and $H^-$), and further include deuterium and its
species ($D$, $D^+$, and $HD$).  
\red{A total of 9 kinetic equations are solved, including 29 kinetic and radiative 
processes, for the 9 species mentioned above.  See Table~\ref{table.collisional} 
for the collisional processes and Table~\ref{table.radiative} for the 
radiative processes solved.}

>>>>

The primordial non-equilibrium chemistry routines used in \enzo\ were
first described by Abel et al. and Anninos et
al. \citep{abel97,anninos97}, but have been extended since then with
updated reaction rates and the inclusion of deuterium species
\citep{2009PhDT.........5T}.  These routines follow the
non-equilibrium chemistry of a gas of primordial composition with 12
total species: $H$, $H^+$, $He$, $He^+$, $He^{++}$, $H^-$, $H_2^+$,
$H_2$, $e^-$, $D$, $D^+$, and $HD$.  (A separate, but related, module
follows the radiative heating and cooling of the gas from atomic and
molecular line excitation, recombination, collisional excitation,
free-free transitions, Compton scattering of the cosmic microwave
background, as well as several models for a metagalactic UV background
that heat the gas via photoionization and discussion -- see
Section~\ref{sec.num.cooling} for more details).  Depending on user
parameters, one can follow simply atomic species ($H$, $H^+$, $He$,
$He^+$, $He^{++}$, and $e^-$), include those relevant for molecular
hydrogen formation ($H_2$, $H_2^+$, and $H^-$), and further include
deuterium and its species ($D$, $D^+$, and $HD$.)  \red{A total of 9
kinetic equations are solved, including 29 kinetic and radiative
processes, for the 9 species mentioned above.  See
Table~\ref{table.collisional} for the collisional processes and
Table~\ref{table.radiative} for the radiative processes solved.}
